Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-19 Codes/PrepareResults.rmd
minor text changes

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  # geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
  # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist +
  theme(legend.title = element_blank())
```

>>>>

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  # geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
  # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist
```

### 2022-03-19 Writing/manuscript_cea.rmd
minor text changes

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulations rounds. Except in the cases of CNN, the figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias. However, the models differed substantially in the accuracy of their treatment effect estimations. Points are clustered more tightly about the 1-to-1 line for CF-base than RF, BRF and CNN. That is, CF-base estimated treatment effects much more efficiently than did RF and BRF, which focus on yield prediction rather than treatment effect estimation.

@@

>>>>

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulations rounds. First of all, CNN suffers from severe underestimation of the impact of N in this particular simulation round. RF also suffers from underestimation of the impact of N. Underestimation of the impact of N generally leads to the underestimation of EONR, which in turn results in profit loss. Underestimation bias from BF is not as severe as RF or CNN. However, unlike RF, BRF, and CNN, points for CF-base clustered around the red 1-to-1 line, meaning that the estimated treatment effects from CF did not exhibit significant bias in treatment effect estimation. Moreover, points are clustered more tightly about the 1-to-1 line for CF-base than BRF. That is, CF-base estimated treatment effects more efficiently than did BRF.

@@

Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix xx as a sensitivity check for interested readers. Basically, qualitative results remain the same.
